Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-02-20 paper.tex
Add Yonglin's new flavor evolution plot

We also solve for the flavor evolution of this system,
integrating $S$ according to Eqn.~\ref{eqn:schroedinger},
as described in \cite{zhu2016-mnr_nsns_remnant}.
In Figs.~\ref{fig:survival-noscat} and \ref{fig:survival-scat}
we show the survival probabilities for $\nu_e$ and $\bar{\nu}_e$
for the two treatments.
\footnote{TODO (Brett, Yonglin): update this paragraph to new compute-eta data}
The survival probabilities are the terms of
the flavor evolution matrix $S$ that describe how much of the original flux
of a given flavor survives a transition.
\footnote{TODO (Yonglin): define $P_{\nu_\alpha\rightarrow\nu_\alpha}$
  in terms of $S$}
Where $P_{\nu_e\rightarrow\nu_e}$ vanishes, for example in
Fig.~\ref{fig:survival-noscat}, all the original $\nu_e$ content of the beam
is oscillated into $\nu_\mu$ and $\nu_\tau$; but the $\nu_e$ density doesn't
vanish altogether,
since some $\nu_\mu$ and $\nu_\tau$ oscillates into $\nu_e$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-noscat_nh}
  % Flavor evolution by Yonglin, see emails 7.19.17-7.20.17
  % Plot: $DIR/31-900kmNHnoScatterPot.eps
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunAB/probabilityPotential
  \caption{Neutrino survival probabilities for the \emph{noscat} case.
    \footnote{TODO (Brett, Yonglin): Replace; this is from the old interp-eta data}
    In the lower panel we reproduce the unoscillated self-interaction potential
    $V_{\nu\nu,0}$ from Fig.~\ref{fig:V_nunu-noscat} and a matter potential
    computed assuming a very simple steady state wind consistent with the
    densities within the simulation volume inside of $r<70$~km
    along this trajectory.
    In this case the neutrinos undergo a symmetric MNR transition
    inside of $r<50$~km,
    with the $e$-flavor neutrinos and antineutrinos fully converting to $\nu_x$.
  }
  \label{fig:survival-noscat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-scat_nh}
  % see notes from fig-survival_prob-noscat_nh
  % Plot: $DIR/130-800kmNHScatterPot.eps (normal hierarchy)
  \caption{Same as Fig.~\ref{fig:survival-noscat},
    but with scattering turned on.
    \footnote{TODO (Brett, Yonglin): Replace; this is from the old interp-eta data}
    In this case the neutrinos undergo a standard MNR transition
    outside of $r>200$~km,
    with the $e$-flavor neutrinos and antineutrinos
    partially converting to $\nu_x$.
    }
  \label{fig:survival-scat}
\end{figure}

>>>>

We also solve for the flavor evolution of this system,
integrating $S$ according to Eqn.~\ref{eqn:schroedinger},
as described in \cite{zhu2016-mnr_nsns_remnant}.
In Fig.~\ref{fig:survival-scat}
we show the survival probabilities for $\nu_e$ and $\bar{\nu}_e$
for the \emph{scat} treatment. (There is no flavor transformation
in the \emph{noscat} treatment.)
The survival probabilities are the terms of
the flavor evolution matrix $S$ that describe how much of the original flux
of a given flavor survives a transition.
\footnote{TODO (Yonglin): define $P_{\nu_\alpha\rightarrow\nu_\alpha}$
  in terms of $S$}
Where $P_{\nu_e\rightarrow\nu_e}$ decreases, for example in
Fig.~\ref{fig:survival-scat} outside of $r\sim400$~km,
a fraction of the original $\nu_e$ content of the beam oscillates into
$\nu_\mu$ and $\nu_\tau$, and a fraction of $\nu_\mu$ and $\nu_\tau$
oscillates into $\nu_e$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-scat_nh}
  % Flavor evolution by Yonglin, see emails 11.28.17 and 1.31.18
  % Plot: $DIR/brett4sfnew300-600kmACC12Step2NE30NH012518m12sc.pdf
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/probabilityPotential-production01
  \caption{Neutrino survival probabilities for the \emph{scat} case.
    In the lower panel we reproduce the self-interaction potential $V_{\nu\nu,0}$
    and matter potential $V_e$ from Fig.~\ref{fig:V_nunu-noscat}.
    \footnote{TODO (Yonglin): change colors and symbols to be consistent with
    text and above plots. Of if you can give me the raw data being plotted, I
    can make the plot.}
    In this case the neutrinos undergo a standard MNR transition
    beginning around $r\sim400$~km,
    with the $e$-flavor neutrinos and antineutrinos partially converting to
    $\nu_x$.
  }
  \label{fig:survival-scat}
\end{figure}
